---
title: "Assignment"
description: |
  This assignment is aim to solve the problems of for Mini Challenge 2
author:
  - name: LI NAN
    url: https://www.linkedin.com/in/li-nan-63b9251a6/
date: 07-12-2021
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
---
<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
#header {
  color: #FF4500;
  background-color: #F5F5F5;
  opacity: 0.6;
  font-family: Calibri;
  font-size: 24px;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
</style>


## 1.Data Preparation

### 1.1 Global Settings

The global settings of R code chunks in this post is set as follows.

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina = 3,
                      echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

### 1.2 R Packages Installation

The following code input is to prepare for R Packages Installation.

```{r}
packages = c('DT', 'ggiraph', 'plotly', 'tidyverse','dplyr','readr')
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}

```



