---
title: "Visualization project"
description: |
  A short description of the post.
author:
  - name: LI NAN
    url: https://www.linkedin.com/in/li-nan-63b9251a6/
date: 08-10-2021
output:
  distill::distill_article:
    self_contained: false
---


### 1.1 Global Settings

The global settings of R code chunks in this post is set as follows. 

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina = 3,
                      echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)

```

### 1.2 R Packages Installation

The following code input is to prepare for R Packages Installation.

```{r}
# !diagnostics off
packages = c('raster','sf','tmap', 'clock','DT', 'ggiraph', 'plotly', 'tidyverse','dplyr','readr','tmap','mapview','geosphere','rgdal','sp','stringdist','fuzzyjoin')
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```


The following code is to import raw data sets from [<font size="3"  color="blue">*Mini Challenge2*</font>](https://vast-challenge.github.io/2021/MC2.html)("*car-assignment.csv*","*cc_data.csv*","*gps.csv*","*loyalty_data.csv*").

```{r}
credit_debit <- read_csv("data/cc_data.csv")
loyalty_data <- read_csv("data/loyalty_data.csv")
car_assignment <- read_csv("data/car_assignments.csv")
GPS <- read_csv("data/gps.csv")

```

### 2.2 Q2 Intruoduction
Add the vehicle data to your analysis of the credit and loyalty card data. How does your assessment of the anomalies in question 1 change based on this new data? What discrepancies between vehicle, credit, and loyalty card data do you find? Please limit your answer to 8 images and 500 words.

#### 2.2.1 Data Preparation for Q2
To proceed in the Q2, we decide to have data manipulation for another two datasets GPS and car_Assignment.

**Data Manipulation for car_Assignment data set and gps data**

```{r}
#Make up the full name
car_assignment1 <-car_assignment %>% unite("Full Name", LastName:FirstName, remove = FALSE)
car_assignment1 <- subset(car_assignment1, select = -c(LastName,FirstName) )
car_assignment1$CarID <- as_factor(car_assignment1$CarID)
```



```{r}
#Basic settings for GPS
#Create (longitude,latitude format)
GPS$Timestamp <- strptime(GPS$Timestamp, "%m/%d/%Y %H:%M:%S")
GPS$day <- as.factor(get_day(GPS$Timestamp))
GPS$id <- as_factor(GPS$id)


GPS_sf <- st_as_sf(GPS, 
                   coords = c("long", "lat"),
                       crs= 4326)#Create (longitude,latitude) for GPS
```

```{r}
#Create gps path
gps_path <- GPS_sf %>%
  group_by(id,day) %>%
  summarize(m = mean(Timestamp), 
            do_union=FALSE) %>%
  st_cast("LINESTRING")





#Delete Orphan route
p = npts(gps_path, by_feature = TRUE)
gps_path2 <- cbind(gps_path, p)
gps_path2 <- dplyr::filter(gps_path2,p!=1)

```

```{r}
glimpse(gps_path)


```




```{r}
#create time delta between points
GPS_sf1<-GPS_sf %>%
  dplyr::arrange(day, Timestamp) %>%
  group_by(id,day) %>%
  mutate(diff = Timestamp - lag(Timestamp),
         diff_mins = as.numeric(diff, units = 'mins'))
#Round to the hundredth place and fill NA
GPS_sf1$diff_mins <- round(GPS_sf1$diff_mins,2)

GPS_sf1 <- GPS_sf1 %>%
  mutate_at(vars(diff_mins), ~replace_na(., 0))

GPS_sf1 <- subset(GPS_sf1, select = -c(diff) )
#Set up Stopping points based on assumption
GPS_sf1$Parking_point<-0
GPS_sf1$Parking_point[GPS_sf1$diff_mins>=5]<-1
GPS_sf1$Parking_point[GPS_sf1$diff_mins<5]<-0
```

```{r}
#GPS_sf1 left join Car_assignment1
GPS_ID <-left_join(GPS_sf1, car_assignment1, by = c("id"="CarID"))

```







```{r}
bgmap <- raster("Data/MC2-tourist.tif")

Abila_st <- st_read(dsn = "Data/Geospatial",
                    layer = "Abila")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255)

```



```{r}


#filter out those points where person stay for more than 5 minutes.
GPS_filter <- GPS_ID %>%
  filter(Parking_point > 0)

#filter out 
GPS_filter$stayperiod<-"Short(0~6)"
GPS_filter$stayperiod[GPS_filter$diff_mins>=360]<-"Long(6+)"
GPS_filter$stayperiod[GPS_filter$diff_mins<360]<-"Short(0~6)"

GPS_home <- GPS_filter %>%
  filter(stayperiod=="Long(6+)")

GPS_park <- GPS_filter %>%
  filter(stayperiod=="Short(0~6)")
```

```{r}
# plot scatter graph in map to find short-time parking locations in the map
gps_path_selected <- gps_path2 %>%
  group_by(id,day)%>%
  filter(id==1,day==14
         )
GPS_filter_day14_id1<-GPS_filter %>%
  group_by(id,day)%>%
  filter(id==1,day==14
         )

tmap_mode("view")
tm_shape(bgmap) + 
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(GPS_filter_day14_id1) +
  tm_dots(col="black",size=0.08)+
  tm_shape(gps_path_selected)+
  tm_lines(col="red")

# plot scatter graph in map to find long-time parking locations in the map
tmap_mode("view")
tm_shape(bgmap) + 
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(GPS_home) +
  tm_dots(col="red",size=0.08)
```



### Transaction data Manipulation

```{r}
loyalty_data$timestamp <- as.Date(loyalty_data$timestamp, "%m/%d/%Y")
loyalty_data$Day <- format(loyalty_data$timestamp, format="%d")

```

```{r}
credit_debit[grep("Katerina", credit_debit$location),2]<- "Katerina's Cafe" 
loyalty_data[grep("Katerina", loyalty_data$location),2]<- "Katerina's Cafe" 
glimpse(credit_debit)

```


```{r}
credit_debit$timestamp <- strptime(credit_debit$timestamp, "%m/%d/%Y %H:%M")
credit_debit$Day <- format(credit_debit$timestamp, format="%d")
credit_debit$hour <- format(credit_debit$timestamp, format="%H")
```



```{r}
# full join and count frequency
cc_loyal <- full_join(credit_debit,loyalty_data,by = c("Day", "location", "price")) %>%
  group_by(last4ccnum, loyaltynum) 

```


```{r}
#delete duplicate column
cc_loyal <- subset(cc_loyal, select = -c(timestamp.y) )


```


```{r}
# inner join and count frequency and regard count>1 is mistake
cc_loyal2 <- inner_join(credit_debit,loyalty_data,by = c("Day", "location", "price")) %>%
  group_by(last4ccnum, loyaltynum) %>%
  summarise(count = n())  %>%
  filter(count>1) 
```

```{r}
#delete loyaltnum column
cc_loyal <- subset(cc_loyal, select = -c(loyaltynum) )


```



```{r}
glimpse(cc_loyal2)
cc_loyal2 <- subset(cc_loyal2, select = -c(count) )

```

```{r}
"change duplicate by combining loyalt num"
cc_loyal2$loyaltynum[1] <- "L3572/L3288"
cc_loyal2$loyaltynum[2] <- "L3572/L3288"

```

```{r}
#delete loyaltnum
#cc_loyal2 =cc_loyal2[-1,]

```


```{r}
#full join cc_loyal2 and credit_debit data frame
cc_loyal3 <- full_join(cc_loyal2,credit_debit,by = "last4ccnum") 


names(cc_loyal3)[names(cc_loyal3) == "price"] <- "cc_price"

#cc_loyal3 <- subset(cc_loyal3, select = -c(count) )!!!!!!!!!
```





```{r}

#有问题，一个人一天去一个地方进行多次消费无法精确匹配
loyalty_data1 <- loyalty_data

loyalty_data1$loyaltynum[loyalty_data$loyaltynum=="L3572"] <- "L3572/L3288"
loyalty_data1$loyaltynum[loyalty_data$loyaltynum=="L3288"] <- "L3572/L3288"


loyalty_data1 <- full_join(cc_loyal2,loyalty_data1,by = "loyaltynum") 
Transaction <- left_join(cc_loyal3,loyalty_data1,by = c("loyaltynum","Day","location","last4ccnum")) 


```






```{r}
datatable(cc_loyal3 ,rownames = FALSE)
```







